---
title: "Homework 4"
subtitle: "ECON 470, Spring 2025"
author: "Ethan Murakami"
format:
  pdf:
    output-file: "murakami_e_hmwk4_s1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

```{r}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```

Here is a link to my repository: {https://github.com/bemur3/hwk4}

\newpage 

```{r}
#| include: false
#| eval: true


load("/Users/ethanmurakami/Documents/GitHub/hwk4/submission1/Hmwk4_workspace.RData")
```


\newpage 


## 1. Remove all SNPs, 800-series plans, and prescription drug only plans (i.e., plans that do not offer Part C benefits). Provide a box and whisker plot showing the distribution of plan counts by county over time. Do you think that the number of plans is sufficient, too few, or too many?

```{r}
#| echo: false


print(plan_counts)
```

\newpage 

## 2. Provide bar graphs showing the distribution of star ratings in 2010, 2012, and 2015. How has this distribution changed over time?

```{r}
#| echo: false
print(star_rating_2010)
print(star_rating_2012)
print(star_rating_2015)
```

\newpage 

## 3. Plot the average benchmark payment over time from 2010 through 2015. How much has the average benchmark payment risen over the years?

```{r}
#| echo: false


print(benchmark_plot)
```

\newpage 

## 4. Plot the average share of Medicare Advantage (relative to all Medicare eligibles) over time from 2010 through 2015. Has Medicare Advantage increased or decreased in popularity? How does this share correlate with benchmark payments?

```{r}
#| echo: false

print(ma_plot)
print(cor_result)
```

\newpage 

## 5. Calculate the running variable underlying the star rating. Provide a table showing the number of plans that are rounded up into a 3-star, 3.5-star, 4-star, 4.5-star, and 5-star rating.

```{r}
#| echo: false


kable(rating_2010, caption = "Number of Plans Rounded to Each Star Rating in 2010")
```

\newpage 

## 6. Using the RD estimator with a bandwidth of 0.125, provide an estimate of the effect of receiving a 3-star versus a 2.5 star rating on enrollments. Repeat the exercise to estimate the effects at 3.5 stars, and summarize your results in a table.

```{r}
#| echo: false

kable(rd_results, caption = "RD Estimates of Star Rating Thresholds on Enrollment")
```
